---
title: "Study 1: analysis and Figure 3"
author: "Seiya Nakata"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
    toc_depth: 2
    number_sections: false
    theme: flatly
    highlight: textmate
    df_print: paged
    fig_caption: true
    fig_width: 8
    fig_height: 4
    keep_md: true
    dev: png
params:
  save_outputs: true
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = "",
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  cache = FALSE,
  tidy = FALSE,
  dpi = 400
)

required_packages <- c("tidyverse", "lmerTest", "patchwork", "knitr")
missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)
]
if (length(missing_packages) > 0) {
  stop(
    "Install the following R packages before knitting: ",
    paste(missing_packages, collapse = ", ")
  )
}

library(tidyverse)
library(lmerTest)
library(patchwork)
library(knitr)

# This Rmd is intended to be stored in Study1/scripts/.
find_project_root <- function() {
  candidates <- unique(normalizePath(c(".", ".."), winslash = "/", mustWork = FALSE))
  for (candidate in candidates) {
    if (dir.exists(file.path(candidate, "data", "processed"))) {
      return(candidate)
    }
  }
  stop(
    "Could not locate Study1/data/processed. ",
    "Place this Rmd in Study1/scripts/ or knit it from Study1/."
  )
}

project_root <- find_project_root()
data_dir <- file.path(project_root, "data", "processed")
results_dir <- file.path(project_root, "results")
figures_dir <- file.path(results_dir, "figures")

dir.create(results_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(figures_dir, recursive = TRUE, showWarnings = FALSE)

# Theme based on the original Study 1 analysis files.
figure_theme <- theme(
  axis.text = element_text(size = 13, family = "Arial", colour = "black"),
  axis.title = element_text(size = 14, family = "Arial", colour = "black"),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  axis.line = element_line(colour = "black", linewidth = 0.45),
  axis.ticks = element_line(colour = "black", linewidth = 0.45),
  plot.tag = element_text(size = 15, family = "Arial", face = "plain"),
  plot.margin = margin(6, 7, 4, 5)
)
```

# Overview

This report reproduces the Study 1 analyses reported in the manuscript from the four processed data files generated by `01_build_study1_data.py`. 

For reproduction accuracy, only actual reproduction trials (Trials 1--8) are analyzed because the independently generated seed at Trial 0 has no observed reproduction accuracy. Hierarchical depth, compression ratio, and dyad similarity are defined for the seed sequences and therefore include Trial 0.

# Load processed data

```{r load-data}
participants <- read.csv(file.path(data_dir, "participants.csv"))
trials <- read.csv(file.path(data_dir, "trials.csv"))
sequence_metrics <- read.csv(file.path(data_dir, "sequence_metrics.csv"))
dyad_similarity <- read.csv(file.path(data_dir, "dyad_similarity.csv"))

required_columns <- list(
  participants = c("participant_id", "dyad_id", "member", "age", "gender"),
  trials = c(
    "participant_id", "dyad_id", "member", "block", "trial_in_block",
    "presented_sequence", "reproduced_sequence"
  ),
  sequence_metrics = c(
    "participant_id", "dyad_id", "member", "block", "trial_in_block",
    "sequence_type", "sequence", "reproduction_accuracy",
    "hierarchical_depth", "compression_ratio"
  ),
  dyad_similarity = c(
    "dyad_id", "block", "trial_in_block", "sequence_type",
    "sequence_member1", "sequence_member2", "dyad_similarity"
  )
)

check_columns <- function(data, columns, name) {
  missing <- setdiff(columns, names(data))
  if (length(missing) > 0) {
    stop(name, " is missing required column(s): ", paste(missing, collapse = ", "))
  }
}

check_columns(participants, required_columns$participants, "participants.csv")
check_columns(trials, required_columns$trials, "trials.csv")
check_columns(sequence_metrics, required_columns$sequence_metrics, "sequence_metrics.csv")
check_columns(dyad_similarity, required_columns$dyad_similarity, "dyad_similarity.csv")
```

# Data validation

```{r validation}
validation_table <- data.frame(
  dataset = c("participants", "trials", "sequence_metrics", "dyad_similarity"),
  rows = c(
    nrow(participants),
    nrow(trials),
    nrow(sequence_metrics),
    nrow(dyad_similarity)
  )
)

kable(validation_table, caption = "Number of rows in each processed dataset")

stopifnot(nrow(participants) == 46)
stopifnot(length(unique(participants$dyad_id)) == 23)
stopifnot(nrow(trials) == 5520)
stopifnot(nrow(sequence_metrics) == 6210)
stopifnot(nrow(dyad_similarity) == 3105)
stopifnot(identical(sort(unique(trials$trial_in_block)), 1:8))
stopifnot(identical(sort(unique(sequence_metrics$trial_in_block)), 0:8))
stopifnot(identical(sort(unique(dyad_similarity$trial_in_block)), 0:8))

# Optional cross-check of reconstructed accuracy against an accuracy
# variable stored in trials.csv. The processed trials file does not need to
# contain such a variable for the manuscript analyses.
accuracy_candidates <- c("logged_accuracy", "otree_accuracy", "accuracy")
available_accuracy_columns <- accuracy_candidates[
  accuracy_candidates %in% names(trials)
]

if (length(available_accuracy_columns) > 0) {

  accuracy_column <- available_accuracy_columns[1]

  trials_accuracy <- trials %>%
    select(
      participant_id, dyad_id, member, block, trial_in_block
    )

  trials_accuracy$recorded_accuracy <- trials[[accuracy_column]]

  accuracy_check <- sequence_metrics %>%
    filter(
      sequence_type == "output",
      !is.na(reproduction_accuracy)
    ) %>%
    select(
      participant_id, dyad_id, member, block, trial_in_block,
      reproduction_accuracy
    ) %>%
    inner_join(
      trials_accuracy,
      by = c(
        "participant_id", "dyad_id", "member",
        "block", "trial_in_block"
      )
    ) %>%
    mutate(
      abs_difference = abs(
        reproduction_accuracy - recorded_accuracy
      )
    )

  max_accuracy_difference <- max(
    accuracy_check$abs_difference,
    na.rm = TRUE
  )

  if (max_accuracy_difference > 1e-6) {
    stop(
      "Accuracy validation failed: ",
      accuracy_column,
      " and reconstructed reproduction_accuracy differ ",
      "by more than 1e-6."
    )
  }

  accuracy_validation_message <- paste0(
    "The reconstructed reproduction accuracy agrees with `",
    accuracy_column,
    "` in trials.csv. Maximum absolute difference = ",
    format(max_accuracy_difference, scientific = TRUE),
    "."
  )

} else {

  max_accuracy_difference <- NA_real_

  accuracy_validation_message <- paste0(
    "No original accuracy column was found in trials.csv. ",
    "The optional cross-check was therefore skipped. ",
    "Reproduction accuracy used in the analysis is the value ",
    "reconstructed from presented and reproduced sequences during ",
    "preprocessing and stored in sequence_metrics.csv."
  )
}

cat(accuracy_validation_message)
```

The processed data contain `r nrow(participants)` participants forming `r length(unique(participants$dyad_id))` dyads. `r accuracy_validation_message`

# Prepare analysis data

```{r prepare-data}
accuracy_data <- sequence_metrics %>%
  filter(
    sequence_type == "output",
    trial_in_block %in% 1:8,
    !is.na(reproduction_accuracy)
  ) %>%
  mutate(dyad_id = factor(dyad_id))

structure_data <- sequence_metrics %>%
  filter(trial_in_block %in% 0:8) %>%
  mutate(dyad_id = factor(dyad_id))

similarity_data <- dyad_similarity %>%
  filter(
    trial_in_block %in% 0:8,
    !is.na(dyad_similarity)
  ) %>%
  mutate(dyad_id = factor(dyad_id))

stopifnot(nrow(accuracy_data) == 5520)
stopifnot(nrow(structure_data) == 6210)
stopifnot(nrow(similarity_data) == 3105)
```

# Descriptive statistics

The original analysis calculated the mean and standard error directly across all observations at each trial position within an interaction block. The same calculation is used here.

```{r descriptives}
mean_se <- function(data, outcome) {
  data %>%
    group_by(trial_in_block) %>%
    summarise(
      mean = mean(.data[[outcome]], na.rm = TRUE),
      sd = sd(.data[[outcome]], na.rm = TRUE),
      n = sum(!is.na(.data[[outcome]])),
      se = sd / sqrt(n),
      .groups = "drop"
    )
}

accuracy_within_block <- mean_se(accuracy_data, "reproduction_accuracy")
hierarchy_within_block <- mean_se(structure_data, "hierarchical_depth")
compression_within_block <- mean_se(structure_data, "compression_ratio")
similarity_within_block <- mean_se(similarity_data, "dyad_similarity")

kable(accuracy_within_block, digits = 4, caption = "Reproduction accuracy by trial")
kable(hierarchy_within_block, digits = 4, caption = "Hierarchical depth by trial")
kable(compression_within_block, digits = 4, caption = "Compression ratio by trial")
kable(similarity_within_block, digits = 4, caption = "Dyad similarity by trial")
```

# Figure 3

The following panels reproduce the appearance of the manuscript figure: black mean lines, grey standard-error bars, no points or grid lines, and the original axis ranges. The dashed line in panel (d) is the mean similarity of the independently generated random seed sequences at Trial 0.

```{r make-panels}
p_accuracy <- ggplot(
  accuracy_within_block,
  aes(x = trial_in_block, y = mean)
) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.10,
    colour = "gray",
    linewidth = 0.40
  ) +
  geom_line(colour = "black", linewidth = 0.50) +
  scale_x_continuous(breaks = c(2, 4, 6, 8), limits = c(1, 8)) +
  scale_y_continuous(
    breaks = seq(0.5, 1.0, 0.1),
    limits = c(0.49, 1.0),
    expand = expansion(mult = c(0, 0.01))
  ) +
  labs(x = "Trial", y = "Accuracy", tag = "(a)") +
  figure_theme

p_hierarchy <- ggplot(
  hierarchy_within_block,
  aes(x = trial_in_block, y = mean)
) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.10,
    colour = "gray",
    linewidth = 0.40
  ) +
  geom_line(colour = "black", linewidth = 0.50) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8), limits = c(0, 8)) +
  scale_y_continuous(
    breaks = seq(1.0, 1.5, 0.1),
    limits = c(1.0, 1.5),
    expand = expansion(mult = c(0, 0.01))
  ) +
  labs(x = "Trial", y = "Depth of hierarchy", tag = "(b)") +
  figure_theme

p_compression <- ggplot(
  compression_within_block,
  aes(x = trial_in_block, y = mean)
) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.10,
    colour = "gray",
    linewidth = 0.40
  ) +
  geom_line(colour = "black", linewidth = 0.50) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8), limits = c(0, 8)) +
  scale_y_continuous(
    breaks = seq(0.50, 0.75, 0.05),
    limits = c(0.50, 0.75),
    expand = expansion(mult = c(0, 0.01))
  ) +
  labs(x = "Trial", y = "Compression ratio", tag = "(c)") +
  figure_theme

random_similarity_baseline <- similarity_within_block %>%
  filter(trial_in_block == 0) %>%
  pull(mean)

p_similarity <- ggplot(
  similarity_within_block,
  aes(x = trial_in_block, y = mean)
) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.10,
    colour = "gray",
    linewidth = 0.40
  ) +
  geom_line(colour = "black", linewidth = 0.50) +
  geom_hline(
    yintercept = random_similarity_baseline,
    linetype = 2,
    colour = "black",
    alpha = 0.50,
    linewidth = 0.45
  ) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8), limits = c(0, 8)) +
  scale_y_continuous(
    breaks = c(0.3, 0.4, 0.5, 0.6),
    limits = c(0.23, 0.65),
    expand = expansion(mult = c(0, 0.01))
  ) +
  labs(x = "Trial", y = "Dyad similarity", tag = "(d)") +
  figure_theme
```

```{r figure3, fig.width=11, fig.height=6.2, fig.cap="Figure 3. (a) Change in reproduction accuracy within an interaction block. (b) Change in hierarchical depth within an interaction block. (c) Change in compression ratio within an interaction block. (d) Change in dyad similarity within an interaction block. Lines show means and error bars show standard errors. The dashed line in panel (d) indicates the mean similarity between the independently generated random seed sequences."}
figure3 <- (p_accuracy | p_hierarchy) / (p_compression | p_similarity) +
  plot_layout(guides = "collect")

figure3

if (isTRUE(params$save_outputs)) {
  # Individual panels, using filenames close to the original analysis.
  ggsave(file.path(figures_dir, "Accuracy.png"), p_accuracy,
         width = 8, height = 4, units = "in", dpi = 400, bg = "white")
  ggsave(file.path(figures_dir, "Depth2.png"), p_hierarchy,
         width = 8, height = 4, units = "in", dpi = 400, bg = "white")
  ggsave(file.path(figures_dir, "Compress.png"), p_compression,
         width = 8, height = 4, units = "in", dpi = 400, bg = "white")
  ggsave(file.path(figures_dir, "DyadSimilarity.png"), p_similarity,
         width = 8, height = 4, units = "in", dpi = 400, bg = "white")

  # Combined manuscript figure.
  ggsave(file.path(figures_dir, "Figure3_Study1.png"), figure3,
         width = 11, height = 6.2, units = "in", dpi = 600, bg = "white")
  ggsave(file.path(figures_dir, "Figure3_Study1.pdf"), figure3,
         width = 11, height = 6.2, units = "in")
}
```

# Linear mixed-effects models

As in the manuscript, trial position within an interaction block is treated as a continuous predictor and dyad is included as a random intercept.

## Reproduction accuracy

```{r model-accuracy}
fit_accuracy <- lmer(
  reproduction_accuracy ~ trial_in_block + (1 | dyad_id),
  data = accuracy_data,
  REML = TRUE
)
summary(fit_accuracy)
```

## Hierarchical depth

```{r model-hierarchy}
fit_hierarchy <- lmer(
  hierarchical_depth ~ trial_in_block + (1 | dyad_id),
  data = structure_data,
  REML = TRUE
)
summary(fit_hierarchy)
```

## Compression ratio

```{r model-compression}
fit_compression <- lmer(
  compression_ratio ~ trial_in_block + (1 | dyad_id),
  data = structure_data,
  REML = TRUE
)
summary(fit_compression)
```

## Dyad similarity

```{r model-similarity}
fit_similarity <- lmer(
  dyad_similarity ~ trial_in_block + (1 | dyad_id),
  data = similarity_data,
  REML = TRUE
)
summary(fit_similarity)
```

# Summary of model results

```{r model-results}
extract_trial_effect <- function(model, outcome, n_obs) {
  coefs <- coef(summary(model))
  trial <- coefs["trial_in_block", ]

  data.frame(
    outcome = outcome,
    n_observations = n_obs,
    beta = unname(trial["Estimate"]),
    SE = unname(trial["Std. Error"]),
    df = unname(trial["df"]),
    t = unname(trial["t value"]),
    p = unname(trial["Pr(>|t|)"])
  )
}

model_results <- bind_rows(
  extract_trial_effect(fit_accuracy, "Reproduction accuracy", nrow(accuracy_data)),
  extract_trial_effect(fit_hierarchy, "Hierarchical depth", nrow(structure_data)),
  extract_trial_effect(fit_compression, "Compression ratio", nrow(structure_data)),
  extract_trial_effect(fit_similarity, "Dyad similarity", nrow(similarity_data))
)

model_results_display <- model_results %>%
  mutate(
    beta = round(beta, 4),
    SE = round(SE, 4),
    df = round(df, 2),
    t = round(t, 2),
    p = ifelse(p < .001, "< .001", sprintf("%.3f", p))
  )

kable(
  model_results_display,
  caption = "Trial effects from the Study 1 linear mixed-effects models"
)

if (isTRUE(params$save_outputs)) {
  write.csv(
    accuracy_within_block,
    file.path(results_dir, "study1_accuracy_descriptives.csv"),
    row.names = FALSE
  )
  write.csv(
    hierarchy_within_block,
    file.path(results_dir, "study1_hierarchy_descriptives.csv"),
    row.names = FALSE
  )
  write.csv(
    compression_within_block,
    file.path(results_dir, "study1_compression_descriptives.csv"),
    row.names = FALSE
  )
  write.csv(
    similarity_within_block,
    file.path(results_dir, "study1_similarity_descriptives.csv"),
    row.names = FALSE
  )
  write.csv(
    model_results,
    file.path(results_dir, "study1_model_results.csv"),
    row.names = FALSE
  )
}
```

# Reproducibility information

```{r save-model-summaries}
if (isTRUE(params$save_outputs)) {
  capture.output(
    {
      cat("STUDY 1 LINEAR MIXED-EFFECTS MODELS\n")
      cat("===================================\n\n")
      cat("1. Reproduction accuracy\n")
      print(summary(fit_accuracy))
      cat("\n\n2. Hierarchical depth\n")
      print(summary(fit_hierarchy))
      cat("\n\n3. Compression ratio\n")
      print(summary(fit_compression))
      cat("\n\n4. Dyad similarity\n")
      print(summary(fit_similarity))
    },
    file = file.path(results_dir, "study1_model_summaries.txt")
  )

  capture.output(
    sessionInfo(),
    file = file.path(results_dir, "session_info.txt")
  )
}

sessionInfo()
```
