---
title: "Study 2: analysis and Figure 4"
author: "Seiya Nakata"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
    toc_depth: 2
    number_sections: false
    theme: flatly
    highlight: textmate
    df_print: paged
    fig_caption: true
    fig_width: 8
    fig_height: 4
    keep_md: true
    dev: png
params:
  save_outputs: true
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = "",
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  cache = FALSE,
  tidy = FALSE,
  dpi = 400
)

required_packages <- c(
  "tidyverse",
  "lmerTest",
  "performance",
  "patchwork",
  "knitr"
)

missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)
]

if (length(missing_packages) > 0) {
  stop(
    "Install the following R packages before knitting: ",
    paste(missing_packages, collapse = ", ")
  )
}

library(tidyverse)
library(lmerTest)
library(performance)
library(patchwork)
library(knitr)

find_project_root <- function() {
  candidates <- unique(
    normalizePath(c(".", ".."), winslash = "/", mustWork = FALSE)
  )

  for (candidate in candidates) {
    if (dir.exists(file.path(candidate, "data", "processed"))) {
      return(candidate)
    }
  }

  stop(
    "Could not locate Study2/data/processed. ",
    "Place this Rmd in Study2/scripts/ or knit it from Study2/."
  )
}

project_root <- find_project_root()
data_dir <- file.path(project_root, "data", "processed")
results_dir <- file.path(project_root, "results")
figures_dir <- file.path(results_dir, "figures")

dir.create(results_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(figures_dir, recursive = TRUE, showWarnings = FALSE)

# This theme follows the original Study 2 plotting scripts.
figure_theme <- theme(
  axis.text = element_text(
    size = 13, family = "Arial", colour = "black"
  ),
  axis.title = element_text(
    size = 14, family = "Arial", colour = "black"
  ),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  axis.line = element_line(colour = "black", linewidth = 0.45),
  axis.ticks = element_line(colour = "black", linewidth = 0.45),
  legend.text = element_text(size = 8, family = "Arial"),
  legend.title = element_text(size = 8, family = "Arial"),
  plot.tag = element_text(
    size = 15, family = "Arial", face = "plain"
  ),
  plot.margin = margin(6, 7, 4, 5)
)

condition_levels <- c(
  "Adult-Adult",
  "Child-Child",
  "Adult-Child"
)

condition_labels <- c(
  "Adult-Adult" = "Adults",
  "Child-Child" = "Children",
  "Adult-Child" = "Adult-Child"
)
```

# Overview

This report reproduces the Study 2 analyses from the four processed datasets generated by `01_build_study2_data.py`. Study 2 compares adult-adult, child-child, and adult-child dyads.

Reproduction accuracy is analyzed for actual reproduction trials only (Trials 1-8 within each interaction block). The independently generated seed at Trial 0 has no observed reproduction accuracy. Hierarchical depth, compression ratio, and dyad similarity are defined for the seed sequences and therefore include Trial 0 in their statistical models.

# Load processed data

```{r load-data}
participants <- read.csv(
  file.path(data_dir, "participants.csv")
)

trials <- read.csv(
  file.path(data_dir, "trials.csv")
)

sequence_metrics <- read.csv(
  file.path(data_dir, "sequence_metrics.csv")
)

dyad_similarity <- read.csv(
  file.path(data_dir, "dyad_similarity.csv")
)

required_columns <- list(
  participants = c(
    "participant_id", "dyad_id", "member",
    "age", "gender", "developmental_group", "condition"
  ),
  trials = c(
    "participant_id", "dyad_id", "member", "condition",
    "block", "trial_in_block", "global_trial",
    "presented_sequence", "reproduced_sequence",
    "logged_accuracy", "reproduction_accuracy"
  ),
  sequence_metrics = c(
    "participant_id", "dyad_id", "member", "condition",
    "block", "trial_in_block", "sequence_type", "sequence",
    "reproduction_accuracy", "hierarchical_depth",
    "compression_ratio"
  ),
  dyad_similarity = c(
    "dyad_id", "condition", "block", "trial_in_block",
    "sequence_type", "sequence_member1", "sequence_member2",
    "dyad_similarity"
  )
)

check_columns <- function(data, columns, name) {
  missing <- setdiff(columns, names(data))

  if (length(missing) > 0) {
    stop(
      name, " is missing required column(s): ",
      paste(missing, collapse = ", ")
    )
  }
}

check_columns(
  participants,
  required_columns$participants,
  "participants.csv"
)

check_columns(
  trials,
  required_columns$trials,
  "trials.csv"
)

check_columns(
  sequence_metrics,
  required_columns$sequence_metrics,
  "sequence_metrics.csv"
)

check_columns(
  dyad_similarity,
  required_columns$dyad_similarity,
  "dyad_similarity.csv"
)
```

# Data validation

```{r validation}
validation_table <- data.frame(
  dataset = c(
    "participants",
    "trials",
    "sequence_metrics",
    "dyad_similarity"
  ),
  rows = c(
    nrow(participants),
    nrow(trials),
    nrow(sequence_metrics),
    nrow(dyad_similarity)
  )
)

kable(
  validation_table,
  caption = "Number of rows in each processed dataset"
)

stopifnot(nrow(participants) == 142)
stopifnot(length(unique(participants$dyad_id)) == 71)
stopifnot(nrow(trials) == 2272)
stopifnot(nrow(sequence_metrics) == 2556)
stopifnot(nrow(dyad_similarity) == 1278)

stopifnot(
  identical(sort(unique(trials$trial_in_block)), 1:8)
)

stopifnot(
  identical(
    sort(unique(sequence_metrics$trial_in_block)),
    0:8
  )
)

stopifnot(
  identical(
    sort(unique(dyad_similarity$trial_in_block)),
    0:8
  )
)

condition_counts <- participants %>%
  distinct(dyad_id, condition) %>%
  count(condition)

kable(
  condition_counts,
  caption = "Number of dyads in each developmental composition"
)

expected_condition_counts <- c(
  "Adult-Adult" = 19L,
  "Child-Child" = 26L,
  "Adult-Child" = 26L
)

observed_condition_counts <- setNames(
  condition_counts$n,
  condition_counts$condition
)[names(expected_condition_counts)]

stopifnot(
  identical(
    as.integer(observed_condition_counts),
    as.integer(expected_condition_counts)
  )
)

# The task-recorded accuracy is stored with finite decimal precision.
# Recomputed values should therefore agree within a small tolerance.
max_accuracy_difference <- max(
  abs(
    trials$logged_accuracy -
      trials$reproduction_accuracy
  ),
  na.rm = TRUE
)

if (max_accuracy_difference > 1e-8) {
  stop(
    "Accuracy validation failed. Maximum absolute difference = ",
    max_accuracy_difference
  )
}

cat(
  "Maximum absolute difference between logged and reconstructed accuracy = ",
  format(max_accuracy_difference, scientific = TRUE),
  ".",
  sep = ""
)
```

# Prepare analysis data

```{r prepare-data}
accuracy_data <- sequence_metrics %>%
  filter(
    sequence_type == "output",
    trial_in_block %in% 1:8,
    !is.na(reproduction_accuracy)
  ) %>%
  mutate(
    dyad_id = factor(dyad_id),
    condition = factor(
      condition,
      levels = condition_levels
    )
  )

structure_data <- sequence_metrics %>%
  filter(trial_in_block %in% 0:8) %>%
  mutate(
    dyad_id = factor(dyad_id),
    condition = factor(
      condition,
      levels = condition_levels
    )
  )

similarity_data <- dyad_similarity %>%
  filter(
    trial_in_block %in% 0:8,
    !is.na(dyad_similarity)
  ) %>%
  mutate(
    dyad_id = factor(dyad_id),
    condition = factor(
      condition,
      levels = condition_levels
    )
  )

stopifnot(nrow(accuracy_data) == 2272)
stopifnot(nrow(structure_data) == 2556)
stopifnot(nrow(similarity_data) == 1278)
```

# Descriptive statistics

The figure uses the same descriptive aggregation as the original analysis: the mean and standard error are calculated across all observations in a developmental-composition condition at each trial position within an interaction block.

```{r descriptives}
mean_se_by_condition <- function(data, outcome) {
  data %>%
    group_by(condition, trial_in_block) %>%
    summarise(
      mean = mean(.data[[outcome]], na.rm = TRUE),
      sd = sd(.data[[outcome]], na.rm = TRUE),
      n = sum(!is.na(.data[[outcome]])),
      se = sd / sqrt(n),
      .groups = "drop"
    )
}

accuracy_plot_data <- mean_se_by_condition(
  accuracy_data,
  "reproduction_accuracy"
)

hierarchy_plot_data <- mean_se_by_condition(
  structure_data %>%
    filter(trial_in_block %in% 1:8),
  "hierarchical_depth"
)

compression_plot_data <- mean_se_by_condition(
  structure_data %>%
    filter(trial_in_block %in% 1:8),
  "compression_ratio"
)

similarity_plot_data <- mean_se_by_condition(
  similarity_data,
  "dyad_similarity"
)

kable(
  accuracy_plot_data,
  digits = 4,
  caption = "Reproduction accuracy by condition and trial"
)

kable(
  hierarchy_plot_data,
  digits = 4,
  caption = "Hierarchical depth by condition and trial"
)

kable(
  compression_plot_data,
  digits = 4,
  caption = "Compression ratio by condition and trial"
)

kable(
  similarity_plot_data,
  digits = 4,
  caption = "Dyad similarity by condition and trial"
)
```

# Figure 4

The color order reproduces the original ggplot2 hue scale: adult-adult dyads are red, child-child dyads are green, and adult-child dyads are blue. Error bars show standard errors.

```{r make-panels}
p_accuracy <- ggplot(
  accuracy_plot_data,
  aes(
    x = trial_in_block,
    y = mean,
    colour = condition,
    group = condition
  )
) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.10,
    colour = "gray",
    linewidth = 0.40
  ) +
  geom_line(linewidth = 0.55) +
  scale_colour_hue(
    name = "condition",
    labels = condition_labels
  ) +
  scale_x_continuous(
    breaks = c(2, 4, 6, 8),
    limits = c(1, 8)
  ) +
  scale_y_continuous(
    breaks = seq(0.5, 1.0, 0.1),
    limits = c(0.49, 1.00),
    expand = expansion(mult = c(0, 0.01))
  ) +
  labs(
    x = "Trial",
    y = "Accuracy",
    tag = "(a)"
  ) +
  figure_theme

p_hierarchy <- ggplot(
  hierarchy_plot_data,
  aes(
    x = trial_in_block,
    y = mean,
    colour = condition,
    group = condition
  )
) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.10,
    colour = "gray",
    linewidth = 0.40
  ) +
  geom_line(linewidth = 0.55) +
  scale_colour_hue(
    name = "condition",
    labels = condition_labels
  ) +
  scale_x_continuous(
    breaks = c(2, 4, 6, 8),
    limits = c(1, 8)
  ) +
  scale_y_continuous(
    breaks = seq(1.0, 1.5, 0.1),
    limits = c(1.0, 1.5),
    expand = expansion(mult = c(0, 0.01))
  ) +
  labs(
    x = "Trial",
    y = "Depth of hierarchy",
    tag = "(b)"
  ) +
  figure_theme

p_compression <- ggplot(
  compression_plot_data,
  aes(
    x = trial_in_block,
    y = mean,
    colour = condition,
    group = condition
  )
) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.10,
    colour = "gray",
    linewidth = 0.40
  ) +
  geom_line(linewidth = 0.55) +
  scale_colour_hue(
    name = "condition",
    labels = condition_labels
  ) +
  scale_x_continuous(
    breaks = c(2, 4, 6, 8),
    limits = c(1, 8)
  ) +
  scale_y_continuous(
    breaks = seq(0.50, 0.75, 0.05),
    limits = c(0.50, 0.75),
    expand = expansion(mult = c(0, 0.01))
  ) +
  labs(
    x = "Trial",
    y = "Compression ratio",
    tag = "(c)"
  ) +
  figure_theme

random_similarity_baseline <- similarity_data %>%
  filter(trial_in_block == 0) %>%
  summarise(mean = mean(dyad_similarity)) %>%
  pull(mean)

p_similarity <- ggplot(
  similarity_plot_data,
  aes(
    x = trial_in_block,
    y = mean,
    colour = condition,
    group = condition
  )
) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.10,
    colour = "gray",
    linewidth = 0.40
  ) +
  geom_line(linewidth = 0.55) +
  geom_hline(
    yintercept = random_similarity_baseline,
    linetype = 2,
    colour = "black",
    alpha = 0.50,
    linewidth = 0.45
  ) +
  scale_colour_hue(
    name = "condition",
    labels = condition_labels
  ) +
  scale_x_continuous(
    breaks = c(0, 2, 4, 6, 8),
    limits = c(0, 8)
  ) +
  scale_y_continuous(
    breaks = c(0.3, 0.4, 0.5, 0.6),
    limits = c(0.23, 0.65),
    expand = expansion(mult = c(0, 0.01))
  ) +
  labs(
    x = "Trial",
    y = "Dyad similarity",
    tag = "(d)"
  ) +
  figure_theme
```

```{r figure4, fig.width=11, fig.height=6.6, fig.cap="Figure 4. (a) Change in reproduction accuracy within an interaction block. (b) Change in hierarchical depth within an interaction block. (c) Change in compression ratio within an interaction block. (d) Change in dyad similarity within an interaction block. Colored lines show condition means and error bars show standard errors. The dashed line in panel (d) indicates the mean similarity between independently generated random seed sequences."}
figure4 <- (
  (p_accuracy | p_hierarchy) /
  (p_compression | p_similarity)
) +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal",
    legend.justification = "center"
  )

figure4

if (isTRUE(params$save_outputs)) {
  ggsave(
    file.path(figures_dir, "Accuracy_cond.png"),
    p_accuracy,
    width = 8,
    height = 4,
    units = "in",
    dpi = 400,
    bg = "white"
  )

  ggsave(
    file.path(figures_dir, "Depth_of_hierarchy2_cond.png"),
    p_hierarchy,
    width = 8,
    height = 4,
    units = "in",
    dpi = 400,
    bg = "white"
  )

  ggsave(
    file.path(figures_dir, "Compression_ratio_cond.png"),
    p_compression,
    width = 8,
    height = 4,
    units = "in",
    dpi = 400,
    bg = "white"
  )

  ggsave(
    file.path(figures_dir, "DyadSimilarity_cond.png"),
    p_similarity,
    width = 8,
    height = 4,
    units = "in",
    dpi = 400,
    bg = "white"
  )

  ggsave(
    file.path(figures_dir, "Figure4_Study2.png"),
    figure4,
    width = 11,
    height = 6.6,
    units = "in",
    dpi = 600,
    bg = "white"
  )

  ggsave(
    file.path(figures_dir, "Figure4_Study2.pdf"),
    figure4,
    width = 11,
    height = 6.6,
    units = "in"
  )
}
```

# Linear mixed-effects models

For each dependent variable, trial position within an interaction block is treated as a continuous predictor. Developmental composition is a categorical predictor with adult-adult dyads as the reference level, and dyad is included as a random intercept. Models with and without the interaction between trial and developmental composition are compared using AIC weights. Because these models differ in their fixed-effects structure, model comparison is performed using maximum-likelihood (ML) fits (`REML = FALSE`). After the better-supported fixed-effects structure is selected, that model is refitted with REML for coefficient estimation.

The reproduction-accuracy model uses Trials 1-8 only. The other three models use Trials 0-8 because those measures are defined for the independently generated seed sequences.

### Estimation strategy

Candidate models that differ in fixed effects are fitted with maximum likelihood (`REML = FALSE`) for AIC comparison. The AIC-supported model is then refitted with restricted maximum likelihood (`REML = TRUE`) for the reported coefficient estimates and Satterthwaite tests.

# Model helper functions

```{r model-helpers}
aic_weight_table <- function(no_interaction, interaction) {
  model_names <- c("No interaction", "Interaction")
  aic_values <- c(
    AIC(no_interaction),
    AIC(interaction)
  )
  delta <- aic_values - min(aic_values)
  weights <- exp(-0.5 * delta)
  weights <- weights / sum(weights)

  data.frame(
    model = model_names,
    AIC = aic_values,
    delta_AIC = delta,
    AIC_weight = weights
  )
}

select_supported_model <- function(no_interaction, interaction) {
  comparison <- aic_weight_table(
    no_interaction,
    interaction
  )

  if (
    comparison$AIC_weight[
      comparison$model == "Interaction"
    ] >
      comparison$AIC_weight[
        comparison$model == "No interaction"
      ]
  ) {
    interaction
  } else {
    no_interaction
  }
}

coefficient_table <- function(model, outcome) {
  coefficients <- as.data.frame(coef(summary(model)))
  coefficients$term <- rownames(coefficients)
  rownames(coefficients) <- NULL

  coefficients %>%
    transmute(
      outcome = outcome,
      term = term,
      beta = Estimate,
      SE = `Std. Error`,
      df = df,
      t = `t value`,
      p = `Pr(>|t|)`
    )
}
```

## Reproduction accuracy

```{r model-accuracy}
fit_accuracy_no_interaction_ml <- lmer(
  reproduction_accuracy ~
    trial_in_block + condition +
    (1 | dyad_id),
  data = accuracy_data,
  REML = FALSE
)

fit_accuracy_interaction_ml <- lmer(
  reproduction_accuracy ~
    trial_in_block * condition +
    (1 | dyad_id),
  data = accuracy_data,
  REML = FALSE
)

accuracy_model_comparison <- aic_weight_table(
  fit_accuracy_no_interaction_ml,
  fit_accuracy_interaction_ml
)

kable(
  accuracy_model_comparison,
  digits = 4,
  caption = "Accuracy model comparison"
)

performance::compare_performance(
  fit_accuracy_no_interaction_ml,
  fit_accuracy_interaction_ml,
  rank = TRUE,
  verbose = FALSE
)

selected_accuracy_model_ml <- select_supported_model(
  fit_accuracy_no_interaction_ml,
  fit_accuracy_interaction_ml
)

# Refit the AIC-supported fixed-effects structure with REML for
# coefficient estimation and Satterthwaite t-tests.
selected_accuracy_model <- update(
  selected_accuracy_model_ml,
  REML = TRUE
)

summary(selected_accuracy_model)
```

## Hierarchical depth

```{r model-hierarchy}
fit_hierarchy_no_interaction_ml <- lmer(
  hierarchical_depth ~
    trial_in_block + condition +
    (1 | dyad_id),
  data = structure_data,
  REML = FALSE
)

fit_hierarchy_interaction_ml <- lmer(
  hierarchical_depth ~
    trial_in_block * condition +
    (1 | dyad_id),
  data = structure_data,
  REML = FALSE
)

hierarchy_model_comparison <- aic_weight_table(
  fit_hierarchy_no_interaction_ml,
  fit_hierarchy_interaction_ml
)

kable(
  hierarchy_model_comparison,
  digits = 4,
  caption = "Hierarchical-depth model comparison"
)

performance::compare_performance(
  fit_hierarchy_no_interaction_ml,
  fit_hierarchy_interaction_ml,
  rank = TRUE,
  verbose = FALSE
)

selected_hierarchy_model_ml <- select_supported_model(
  fit_hierarchy_no_interaction_ml,
  fit_hierarchy_interaction_ml
)

# Refit the AIC-supported fixed-effects structure with REML for
# coefficient estimation and Satterthwaite t-tests.
selected_hierarchy_model <- update(
  selected_hierarchy_model_ml,
  REML = TRUE
)

summary(selected_hierarchy_model)
```

## Compression ratio

```{r model-compression}
fit_compression_no_interaction_ml <- lmer(
  compression_ratio ~
    trial_in_block + condition +
    (1 | dyad_id),
  data = structure_data,
  REML = FALSE
)

fit_compression_interaction_ml <- lmer(
  compression_ratio ~
    trial_in_block * condition +
    (1 | dyad_id),
  data = structure_data,
  REML = FALSE
)

compression_model_comparison <- aic_weight_table(
  fit_compression_no_interaction_ml,
  fit_compression_interaction_ml
)

kable(
  compression_model_comparison,
  digits = 4,
  caption = "Compression-ratio model comparison"
)

performance::compare_performance(
  fit_compression_no_interaction_ml,
  fit_compression_interaction_ml,
  rank = TRUE,
  verbose = FALSE
)

selected_compression_model_ml <- select_supported_model(
  fit_compression_no_interaction_ml,
  fit_compression_interaction_ml
)

# Refit the AIC-supported fixed-effects structure with REML for
# coefficient estimation and Satterthwaite t-tests.
selected_compression_model <- update(
  selected_compression_model_ml,
  REML = TRUE
)

summary(selected_compression_model)
```

## Dyad similarity

```{r model-similarity}
fit_similarity_no_interaction_ml <- lmer(
  dyad_similarity ~
    trial_in_block + condition +
    (1 | dyad_id),
  data = similarity_data,
  REML = FALSE
)

fit_similarity_interaction_ml <- lmer(
  dyad_similarity ~
    trial_in_block * condition +
    (1 | dyad_id),
  data = similarity_data,
  REML = FALSE
)

similarity_model_comparison <- aic_weight_table(
  fit_similarity_no_interaction_ml,
  fit_similarity_interaction_ml
)

kable(
  similarity_model_comparison,
  digits = 4,
  caption = "Dyad-similarity model comparison"
)

performance::compare_performance(
  fit_similarity_no_interaction_ml,
  fit_similarity_interaction_ml,
  rank = TRUE,
  verbose = FALSE
)

selected_similarity_model_ml <- select_supported_model(
  fit_similarity_no_interaction_ml,
  fit_similarity_interaction_ml
)

# Refit the AIC-supported fixed-effects structure with REML for
# coefficient estimation and Satterthwaite t-tests.
selected_similarity_model <- update(
  selected_similarity_model_ml,
  REML = TRUE
)

summary(selected_similarity_model)
```

# Model summaries

```{r model-summary}
model_comparison_summary <- bind_rows(
  accuracy_model_comparison %>%
    mutate(outcome = "Reproduction accuracy"),
  hierarchy_model_comparison %>%
    mutate(outcome = "Hierarchical depth"),
  compression_model_comparison %>%
    mutate(outcome = "Compression ratio"),
  similarity_model_comparison %>%
    mutate(outcome = "Dyad similarity")
) %>%
  select(
    outcome,
    model,
    AIC,
    delta_AIC,
    AIC_weight
  )

selected_model_coefficients <- bind_rows(
  coefficient_table(
    selected_accuracy_model,
    "Reproduction accuracy"
  ),
  coefficient_table(
    selected_hierarchy_model,
    "Hierarchical depth"
  ),
  coefficient_table(
    selected_compression_model,
    "Compression ratio"
  ),
  coefficient_table(
    selected_similarity_model,
    "Dyad similarity"
  )
)

kable(
  model_comparison_summary,
  digits = 4,
  caption = "AIC comparison of ML-fitted models with and without interactions"
)

kable(
  selected_model_coefficients,
  digits = 4,
  caption = "Coefficients from the AIC-supported model for each outcome"
)
```

# Save analysis outputs

```{r save-outputs}
if (isTRUE(params$save_outputs)) {
  write.csv(
    accuracy_plot_data,
    file.path(
      results_dir,
      "study2_accuracy_descriptives.csv"
    ),
    row.names = FALSE
  )

  write.csv(
    hierarchy_plot_data,
    file.path(
      results_dir,
      "study2_hierarchy_descriptives.csv"
    ),
    row.names = FALSE
  )

  write.csv(
    compression_plot_data,
    file.path(
      results_dir,
      "study2_compression_descriptives.csv"
    ),
    row.names = FALSE
  )

  write.csv(
    similarity_plot_data,
    file.path(
      results_dir,
      "study2_similarity_descriptives.csv"
    ),
    row.names = FALSE
  )

  write.csv(
    model_comparison_summary,
    file.path(
      results_dir,
      "study2_model_comparisons.csv"
    ),
    row.names = FALSE
  )

  write.csv(
    selected_model_coefficients,
    file.path(
      results_dir,
      "study2_selected_model_coefficients.csv"
    ),
    row.names = FALSE
  )

  capture.output(
    {
      cat("STUDY 2 LINEAR MIXED-EFFECTS MODELS\n")
      cat("===================================\n\n")

      cat("1. Reproduction accuracy\n")
      print(summary(selected_accuracy_model))

      cat("\n\n2. Hierarchical depth\n")
      print(summary(selected_hierarchy_model))

      cat("\n\n3. Compression ratio\n")
      print(summary(selected_compression_model))

      cat("\n\n4. Dyad similarity\n")
      print(summary(selected_similarity_model))
    },
    file = file.path(
      results_dir,
      "study2_model_summaries.txt"
    )
  )

  capture.output(
    sessionInfo(),
    file = file.path(
      results_dir,
      "session_info.txt"
    )
  )
}
```

# Session information

```{r session-info}
sessionInfo()
```
